Containers and R---the Rockerverse and beyond

### 2020-01-10 manuscript.Rmd
add list of not included projects to README

<!--
**docker** ([https://bhaskarvk.github.io/docker](https://bhaskarvk.github.io/docker)
docker has been removed from CRAN, seems unmaintained by authors. Maybe it should be removed from this list?
-->

This requires stepping out of the R ecosystem and into an infrastructure mindset where the user needs to specify the environment they require.
Because `Dockerfile`s can be read as a series of steps, this lends itself well to the `tidyverse` style of programming where each step is piped into the next.
dockyard has a `Dockerfile` object that either starts out as an empty `Dockerfile`, or can use existing `Dockerfile` to use as a template.
This combined with a series of functions that are analogous to the steps commonly found in a `Dockerfile`, it makes building Docker images much more approachable to R users.
There are also wrappers for commonly used steps for R programmers like adding libraries and copying files into the R Docker containers.
Once the `Dockerfile` is created, dockyard has the functionality to build the image and deploy it.

>>>>

**dockyard** ([https://github.com/thebioengineer/dockyard](https://github.com/thebioengineer/dockyard)) has the goal of lowering barrier to creating `Dockerfile`s and Docker images, and deploying Docker containers. 
The way docker images are made is by reading and following a set of instructions found in `Dockerfile`s.
This requires stepping out of the R ecosystem and into an infrastructure mindset where the user needs to specify the environment they require.
Because `Dockerfile`s can be read as a series of steps, this lends itself well to the `tidyverse` style of programming where each step is piped into the next.
dockyard has a `Dockerfile` object that either starts out as an empty `Dockerfile`, or can use existing `Dockerfile` to use as a template.
This combined with a series of functions that are analogous to the steps commonly found in a `Dockerfile`, it makes building Docker images much more approachable to R users.
There are also wrappers for commonly used steps for R programmers like adding libraries and copying files into the R Docker containers.
Once the `Dockerfile` is created, dockyard has the functionality to build the image and deploy it.
